Type Error Telemetry at Scale

### 2023-09-30 programming23/paper.tex
fix undef ref, clear 4.6 todos

\Cref{t:type-error-count} reports the percent of type errors that overlap with
the edit range.\todo{I DO NOT UNDERSTAND ANYTHING HERE.}
The purpose of this table is to discover all specific errors in the dataset,
thus it includes both keystroke-based and module-switch-based records---even
though edit ranges are not well-defined for the latter.

There are two subtables for \mnonstrict{} and \mstrict{} mode.
The table does not report \mnocheck{} because all its type errors are
by definition \code{SyntaxError}s.

@@

\begin{itemize}
  \item
    Syntax errors, in particular \code{UnknownSymbol}, are much more
    common in \mnonstrict{} than \mstrict{}.\todo{This is NOT a
      ``syntax'' error? It's a typo!}
    This may be because \mnonstrict{} reports fewer errors in general.

@@

\subsection{Do Edits Tend to Add Type Errors?}
\label{s:tefs-compass}

>>>>

\Cref{t:type-error-count} sorts type errors by their popularity
in \mnonstrict{} and \mstrict{} mode.
The purpose of this table is to discover and rank all errors that
appear in the dataset, thus it is based on both keystroke and
module-switch telemetry records even though edit ranges are not well-defined
for the latter.
The table does not include \mnocheck{} because all its type errors are
\code{SyntaxError}s by definition.

@@

\begin{itemize}
  \item
    Syntax errors, in particular \code{UnknownSymbol} (for an unbound variable),
    are much more common in \mnonstrict{} than \mstrict{}.
    This may be because \mnonstrict{} reports fewer errors
    to dilute the proportion of unknown symbols.

@@

\subsection{Do Edits Tend to Add Type Errors?}
\label{s:tefs-compass}
\label{s:strict-vs-forcedstrict}
